---
title: "Intercoder agreement 2"
author: "Chloé Vincent"
date: "24-MAR-2022"
output: html_document
---
<!-- In order to use this file for a new intercoder test, here is the list of lines to modify:
- lines 2 to 4 title, author and date
- line 117 Description of the report
- line 160 example of how the calculation is done - this line can also be simply removed

the "censored info file" needs to be modified depending on who is taking part in the test and if the MAXQDA pseudonyms changed
-->


<!-- The option "cache=TRUE" in the code chunks getFunctionHelper and getDataframes
avoid calling the "choose.files" function which opens a window each time the script runs -->
```{r getFunctionHelper, include=FALSE}
RFilter <- matrix(c("R files (*.R)", "*.R"), nrow = 1)
  functionHelperPath <- choose.files(default = "", 
                                     caption = "Select the function helper",
                                     filters = RFilter,
                                     index = 1)
  censoredInfoPath <- choose.files(default = "",
                                     caption = "Select the Censored Info file",
                                     filters = RFilter,
                                     index = 1)
```

```{r sourceFunctionHelper, include=FALSE}

source(functionHelperPath)
```

```{r getDataframes, include=FALSE}
# read the CSV file
#   Export the Maxqda project file (Reports > Export > “Projects components as Excel File”), 
#   open this Excel file to the “Coded segments” sheet and “Save as CSV” 
#   (you will get an alert that it will save only the active sheet).
df <- getMaxqdaCSVExport()

df.calc <- getResultTable(df, FALSE)

df.summary <- getSummary(df.calc)

df.sum.reduced <- getResultTable(df, TRUE) %>%
                    getSummary()

```
```{r formatTables, include=FALSE}
library("reactable")
#library(RColorBrewer)
# the viridis package is only needed for the pretty colors, you can use a list of colors
# to replace the argument of "make_color_pal" (e.g. c("#ffffff", "#f2fbd2",...))
library("viridis")
make_color_pal <- function(colors, bias = 1) {
  get_color <- colorRamp(colors, bias = bias)
  function(x) rgb(get_color(x), alpha= 150, maxColorValue = 255)
}

agreement_pct_color <- make_color_pal(magma(10))

#brewer.pal(11,'RdYlGn')
#brewer.pal(11,'RdYlBu')
#brewer.pal(11,'Spectral')
#c("#ffffff", "#f2fbd2", "#c9ecb4", "#93d3ab", "#35b0ab")

format_pct <- function(value) {
  if (is.na(value)){
        ""
  }else{
    formatC(paste0(round(value * 100, digits=2), "%"), width = 4)
  }
}
agreement_column <- function(class = NULL, ...) {
  colDef(
    cell = format_pct,
    class = paste("cell number", class),
    style = function(value) {
      # Lighter color for <1% (kept for the example)
      if (is.na(value)){
        list(color ="#fff")
      }else if (value < 0.01) {
        list(color = "#aaa")
      } else {
        list(color = "#111", background = agreement_pct_color(value))
      }
    },
    ...
  )
}

code_column <- function(){
    colDef(
    style = function(value) {
      if (is.na(value)){
        list(color ="#000")
      }else if (substring(value,1,2) =="I0") {
        list(color = "#0cbfcc", fontWeight = "bold")
      } else if (substring(value,1,2) == "I1") {
        list(color = "#961e96", fontWeight = "bold")
      }
    },
  )
}

comment_column <- function(){
    colDef(
      name = "View comments",
      cell = function() htmltools::tags$button("view")
      )
}

```



## Summary

This intercoder agreement test is based on comments taken from the Independant Facebook post [Amnesty accuses Israel of being an ‘apartheid’ state](https://www.facebook.com/TheIndependentOnline/posts/10159970276036636).

```{r summary, echo=FALSE}
reactable(df.summary,
          columns = eval(parse(text=getAgreementListColumnToEval())))
```

#### AS vs. not AS

Agreement results when the difference between I0 vs. I0c and I1 vs. I1ASC are ignored:
```{r reduced, echo=FALSE}
reactable(df.sum.reduced,
          columns = eval(parse(text=getAgreementListColumnToEval())))
```

## Result table

<!-- Note that the last line (647) was not filtered out, even though it's the 51st comment coded, because more than half of the coders did code it and it didn't change the final results much. -->
Note that when double coded differently I only counted half the 'point'.<br/>
E.g. (I1) and (I1, I1a) is 0.5 ; (I1ASC, I1a) and (I1a, I1ASC) is 1

```{r results, echo=FALSE}
reactable(df.calc %>% 
            select(End, all_of(codersNames), commentAgreement, commentAgreement.red, Segment)%>%
            rename("Line #"= End),
          pagination = FALSE,
          fullWidth = FALSE,
          columns = eval(parse(text=getCodeListColumnToEval())),

          onClick = JS("function(rowInfo, colInfo) {
    // Only handle click events on the 'Segment' column
    if (colInfo.id !== 'Segment') {
      return
    }

    // Display an alert dialog with details for the row
    window.alert(rowInfo.row['Segment'] )
  }")          
          
)

```
\* The percentage is the mean of the agreements of all the coders' pairs. <br/>
 E.g. for line 77: 15 pairs agree out of 28 possibilities, i.e. 15/28= 53.57% of mean agreement for the comment line 77.
